### 2022-12-03 ms.rmd
Fixed name

###################################################
# Model 3.2: Model controlling for acclimation time, 
# type and habitat assuming type can vary by habitat
###################################################
rerun = TRUE
if(rerun){
  # More realistic model with 
  model3.1          <- metafor::rma.mv(effect_size ~ c_accl_time + type + habitat + type:habitat, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild)

>>>>

###################################################
# Model 3.2: Model controlling for acclimation time, 
# type and habitat assuming type can vary by habitat
###################################################
rerun = TRUE
if(rerun){
  # More realistic model with 
  model3.2          <- metafor::rma.mv(effect_size ~ c_accl_time + type + habitat + type:habitat, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild)
